%==============================================================================
%  Curriculum Vitae  --  Adam Smith  (FICTITIOUS / DEMO CV)
%  Field: Economics  |  Based in Stockholm, Sweden
%  Compile with: pdflatex adam_smith_cv.tex   (run twice for hyperlinks)
%==============================================================================
\documentclass[11pt]{article}

% --- Encoding & font -------------------------------------------------------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{mathpazo}                 % Palatino: elegant, reliably available

% --- Layout ----------------------------------------------------------------
\usepackage[a4paper,margin=1in,headheight=14pt]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[hidelinks]{hyperref}

% --- Colors ----------------------------------------------------------------
\definecolor{accent}{HTML}{1F3A5F}    % deep navy
\definecolor{rulegray}{HTML}{B0B7C0}
\definecolor{mutedgray}{HTML}{555B66}

\hypersetup{
  colorlinks=true,
  urlcolor=accent,
  linkcolor=accent,
  pdftitle={Adam Smith --- Curriculum Vitae},
  pdfauthor={Adam Smith}
}

% --- Section formatting ----------------------------------------------------
\titleformat{\section}
  {\large\scshape\bfseries\color{accent}}
  {}{0em}{}[\vspace{2pt}{\color{rulegray}\titlerule[1pt]}]
\titlespacing*{\section}{0pt}{16pt}{8pt}

\titleformat{\subsection}
  {\normalsize\itshape\color{mutedgray}}
  {}{0em}{}
\titlespacing*{\subsection}{0pt}{8pt}{4pt}

% --- List styling ----------------------------------------------------------
\setlist[itemize]{leftmargin=1.4em,itemsep=3pt,topsep=3pt,parsep=0pt}
\newlist{cvlist}{itemize}{1}
\setlist[cvlist]{label=,leftmargin=0em,itemsep=6pt,topsep=2pt,parsep=0pt}

% --- Helper macros ----------------------------------------------------------
% Two-column dated entry: \dated{year}{description}
\newcommand{\dated}[2]{%
  \noindent\makebox[5.2em][l]{\textcolor{mutedgray}{#1}}%
  \begin{minipage}[t]{\dimexpr\linewidth-5.4em\relax}#2\end{minipage}\par\vspace{3pt}}

% Publication / paper item with hanging indent
\newcommand{\pubitem}[1]{\item #1}

% Header / footer
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\footnotesize\textcolor{mutedgray}{Adam Smith \textbullet\ Curriculum Vitae}}
\fancyfoot[R]{\footnotesize\textcolor{mutedgray}{Page \thepage\ of \pageref{LastPage}}}
\fancyfoot[C]{\footnotesize\textcolor{mutedgray}{Last updated: June 2026}}

\setlength{\parindent}{0pt}

%==============================================================================
\begin{document}

% ---------------------------------------------------------------- HEADER ----
\begin{center}
  {\Huge\bfseries\color{accent} Adam Smith}\\[6pt]
  {\large\scshape Professor of Economics}\\[8pt]
  {\color{rulegray}\rule{0.55\linewidth}{0.8pt}}\\[8pt]
  \normalsize
  Department of Economics, Stockholm University\\
  Universitetsv\"agen 10A, SE-106 91 Stockholm, Sweden\\[4pt]
  \href{mailto:adam.smith@su.se}{adam.smith@su.se} \quad\textbullet\quad
  \href{https://www.su.se/english/profiles/adsm-economics}{su.se/profiles/adam-smith} \quad\textbullet\quad
  +46 (0)8 16 20 00
\end{center}

\vspace{4pt}

% ------------------------------------------------------ RESEARCH FIELDS ----
\section{Research Interests}
Public economics; labor economics; economics of taxation and inequality;
social insurance; economics of education. Empirical work combining
administrative register data with quasi-experimental and structural methods.

% --------------------------------------------------------- APPOINTMENTS ----
\section{Academic Appointments}
\dated{2021--}{\textbf{Professor of Economics}, Stockholm University}
\dated{2016--21}{\textbf{Associate Professor (Docent)}, Stockholm School of Economics}
\dated{2011--16}{\textbf{Assistant Professor}, Uppsala University}
\dated{2014}{\textbf{Visiting Scholar}, University of California, Berkeley (Spring)}

\subsection{Research Affiliations}
\dated{2019--}{Research Fellow, Centre for Economic Policy Research (CEPR), London}
\dated{2017--}{Research Affiliate, IZA Institute of Labor Economics, Bonn}
\dated{2018--}{Network Member, CESifo, Munich}
\dated{2020--}{Affiliated Researcher, Uppsala Center for Fiscal Studies (UCFS)}

% ------------------------------------------------------------ EDUCATION ----
\section{Education}
\dated{2011}{\textbf{Ph.D. in Economics}, Massachusetts Institute of Technology (MIT)\\
  Dissertation: \emph{Three Essays on Taxation, Labor Supply, and Inequality}\\
  Committee: Esther Duflo (chair), James Poterba, Amy Finkelstein}
\dated{2006}{\textbf{M.Sc. in Economics}, London School of Economics (LSE), with Distinction}
\dated{2004}{\textbf{B.Sc. in Economics}, Stockholm University, summa cum laude}

% ------------------------------------------------------- PUBLICATIONS ----
\section{Publications in Peer-Reviewed Journals}
\begin{cvlist}
\pubitem{``Marginal Tax Rates and the Elasticity of Taxable Income: Evidence from a Swedish Reform,'' with Johanna Lindqvist. \emph{American Economic Review}, 2025, 115(4): 1102--1147.}
\pubitem{``Wealth Taxation and Capital Flight: Register Evidence from the Nordic Abolition,'' with Henrik Berg and Maria Olsson. \emph{Quarterly Journal of Economics}, 2024, 139(2): 845--901.}
\pubitem{``The Long-Run Effects of Parental Leave on Earnings and Fertility,'' with Sofia Eriksson. \emph{Journal of Political Economy}, 2023, 131(9): 2410--2458.}
\pubitem{``Place-Based Subsidies and Local Labor Markets,'' with Lars Petersson. \emph{Econometrica}, 2022, 90(6): 2733--2779.}
\pubitem{``Optimal Unemployment Insurance over the Business Cycle,'' with Johanna Lindqvist. \emph{Review of Economic Studies}, 2022, 89(3): 1455--1499.}
\pubitem{``Inheritance, Mobility, and the Transmission of Wealth across Generations,'' with Henrik Berg. \emph{Journal of Public Economics}, 2021, 198: 104--421.}
\pubitem{``Minimum Wages and Firm Dynamics in Retail,'' with Anna Nyberg and Carlos Mendez. \emph{American Economic Journal: Applied Economics}, 2020, 12(4): 213--251.}
\pubitem{``Tax Salience and Consumer Responses to Value-Added Taxation,'' with Sofia Eriksson. \emph{Journal of Public Economics}, 2019, 176: 32--49.}
\pubitem{``Schooling, Skills, and the Gender Wage Gap in Sweden,'' with Maria Olsson. \emph{Labour Economics}, 2018, 53: 88--106.}
\pubitem{``Behavioral Responses to Pension Reform: Evidence from Notional Defined Contributions,'' with Lars Petersson. \emph{Journal of Human Resources}, 2017, 52(3): 701--739.}
\pubitem{``The Incidence of Payroll Taxes: Evidence from a Regional Discontinuity,'' \emph{American Economic Journal: Economic Policy}, 2016, 8(2): 1--34.}
\pubitem{``Income Inequality and Intergenerational Mobility: A Cross-Country Perspective,'' with Johanna Lindqvist and Henrik Berg. \emph{Economic Journal}, 2014, 124(577): 678--712.}
\end{cvlist}

% ------------------------------------------------------- WORKING PAPERS ----
\section{Working Papers}
\begin{cvlist}
\pubitem{``Carbon Taxes, Commuting, and the Distribution of Welfare,'' with Sofia Eriksson and Carlos Mendez (revise and resubmit, \emph{American Economic Review}), 2026.}
\pubitem{``Top Incomes and the Race between Education and Technology,'' with Henrik Berg, NBER Working Paper No.\ 33812, 2026.}
\pubitem{``Childcare Subsidies and Maternal Labor Supply: A Structural Evaluation,'' with Sofia Eriksson, CEPR Discussion Paper No.\ 19204, 2025.}
\pubitem{``Wealth Concealment and Enforcement: Evidence from the Panama Papers,'' with Maria Olsson, IZA Discussion Paper No.\ 17455, 2025.}
\pubitem{``The Geography of Social Mobility in Sweden,'' with Lars Petersson, 2025.}
\end{cvlist}

% ------------------------------------------------------- WORK IN PROGRESS ---
\section{Work in Progress}
\begin{cvlist}
\pubitem{``Automation, Reallocation, and the Welfare State'' (with Johanna Lindqvist).}
\pubitem{``Universal Basic Income: Evidence from a Municipal Pilot'' (with Anna Nyberg).}
\pubitem{``Tax Audits and Voluntary Compliance: A Field Experiment with the Swedish Tax Agency'' (data collection in progress).}
\end{cvlist}

% --------------------------------------------------- GRANTS & FELLOWSHIPS ---
\section{Grants and Fellowships}
\dated{2024--29}{European Research Council (ERC) Consolidator Grant, \emph{``The Distributional Consequences of Tax Policy''} (EUR\,2.0M). Principal Investigator.}
\dated{2022--26}{Swedish Research Council (Vetenskapsr\aa det) Project Grant (SEK 6.4M). PI.}
\dated{2020--23}{Riksbankens Jubileumsfond Research Grant (SEK 4.1M). Co-PI with H.\ Berg.}
\dated{2018--21}{Forte (Swedish Research Council for Health, Working Life and Welfare) Grant (SEK 3.2M). PI.}
\dated{2010--11}{MIT Presidential Graduate Fellowship.}

% ----------------------------------------------------------- HONORS ----
\section{Honors and Awards}
\dated{2025}{Assar Lindbeck Medal, Swedish Economic Association.}
\dated{2024}{Best Paper Award, International Institute of Public Finance (IIPF) Annual Congress.}
\dated{2023}{Excellence in Teaching Award, Stockholm University Faculty of Social Sciences.}
\dated{2019}{Young Economist Award, European Economic Association.}
\dated{2011}{Robert M.\ Solow Prize for Best Dissertation in Economics, MIT.}

% ------------------------------------------------------- INVITED TALKS ----
\section{Invited Seminars (Selected)}
\begin{itemize}
\item Harvard University; MIT; UC Berkeley; University of Chicago; Princeton University (2018--2026).
\item London School of Economics; University College London; University of Oxford; Bocconi University (2017--2025).
\item Paris School of Economics; Toulouse School of Economics; University of Zurich; University of Munich (LMU) (2016--2024).
\item Stockholm School of Economics; Uppsala University; University of Oslo; University of Copenhagen; Aarhus University (2015--2026).
\item Institute for International Economic Studies (IIES); IFAU; Norwegian School of Economics (NHH) (2014--2025).
\end{itemize}

% -------------------------------------------------- CONFERENCE PRESENTATIONS ---
\section{Conference Presentations (Selected)}
\begin{itemize}
\item NBER Summer Institute (Public Economics), Cambridge MA --- 2019, 2022, 2024, 2026.
\item Annual Congress of the European Economic Association (EEA) --- 2017, 2019, 2021, 2023, 2025.
\item International Institute of Public Finance (IIPF) Annual Congress --- 2018, 2021, 2024 (keynote).
\item Society of Labor Economists (SOLE) Annual Meeting --- 2018, 2020, 2023.
\item NBER--CEPR International Seminar on Macroeconomics (ISOM) --- 2022.
\item CESifo Area Conference on Public Economics, Munich --- 2017, 2020, 2023, 2025.
\item Royal Economic Society (RES) Annual Conference --- 2016, 2019, 2022.
\item Nordic Summer Symposium in Macroeconomics (invited) --- 2021, 2024.
\end{itemize}

% --------------------------------------------------- SELECTED MEDIA COVERAGE ---
\section{Selected Media Coverage}
Research featured in international and Swedish media outlets:
\begin{itemize}
\item ``Does Taxing the Rich Drive Them Away? New Evidence Says No.'' \emph{The New York Times}, March 2024.
\item ``The Nordic Wealth-Tax Experiment.'' \emph{The Economist}, April 2024.
\item ``Parental Leave Pays Off for Decades, Study Finds.'' \emph{Financial Times}, September 2023.
\item ``What Sweden Learned About Place-Based Subsidies.'' \emph{Bloomberg}, July 2022.
\item ``Why Higher Minimum Wages Didn't Kill Retail Jobs.'' \emph{The Guardian}, May 2020.
\item ``Forskaren som r\"aknar p\aa\ skatterna'' (The researcher who does the math on taxes). \emph{Dagens Nyheter}, January 2025.
\item ``Ny studie: f\"or\"aldraledighet l\"onar sig p\aa\ l\aa ng sikt.'' \emph{Svenska Dagbladet}, September 2023.
\item Interview on tax reform, \emph{SVT Aktuellt} (Swedish national television), November 2024.
\item ``Sweden's Inequality Debate, Explained.'' \emph{Vox}, February 2023.
\item Cited in \emph{The Wall Street Journal} editorial on capital taxation, June 2024.
\end{itemize}

% --------------------------------------------------- OP-EDS & PUBLIC WRITING ---
\section{Op-Eds and Public Writing}
\begin{itemize}
\item ``The Case for a Simpler Tax Code,'' \emph{Dagens Nyheter} (DN Debatt), 2025.
\item ``Rethinking Wealth Taxation in an Open Economy,'' \emph{VoxEU/CEPR}, 2024.
\item ``Childcare Is Economic Policy,'' \emph{Project Syndicate}, 2023.
\item ``What the Data Really Say About Minimum Wages,'' \emph{Ekonomisk Debatt}, 2021.
\end{itemize}

\subsection{Podcasts and Interviews}
\begin{itemize}
\item Guest, \emph{Freakonomics Radio}, episode on taxation and behavior, 2024.
\item Guest, \emph{The Economics Show} (BBC Radio 4), 2023.
\item Guest, \emph{P1 Morgon} (Sveriges Radio), recurring commentator on fiscal policy, 2022--present.
\end{itemize}

% ----------------------------------------------------------- TEACHING ----
\section{Teaching}
\subsection{Stockholm University}
\begin{itemize}
\item Public Economics (Ph.D.) --- 2021--present.
\item Empirical Methods in Economics (M.Sc.) --- 2021--present.
\item Principles of Microeconomics (B.Sc.) --- 2021--2023.
\end{itemize}
\subsection{Stockholm School of Economics \& Uppsala University}
\begin{itemize}
\item Labor Economics (M.Sc.); Taxation and Public Policy (M.Sc.); Intermediate Microeconomics (B.Sc.).
\end{itemize}

% ----------------------------------------------------------- ADVISING ----
\section{Ph.D. Advising}
\subsection{Primary Advisor}
\begin{itemize}
\item Emil Karlsson (2024) --- first placement: Norwegian School of Economics (NHH).
\item Priya Nair (2023) --- first placement: Ministry of Finance, Sweden.
\item Tomas Andersson (2021) --- first placement: IFAU.
\end{itemize}
\subsection{Committee Member}
\begin{itemize}
\item Eight additional dissertation committees at Stockholm University, SSE, and Uppsala (2017--present).
\end{itemize}

% ----------------------------------------------------- PROFESSIONAL SERVICE ---
\section{Professional Service}
\subsection{Editorial}
\begin{itemize}
\item Associate Editor, \emph{Journal of Public Economics} (2023--present).
\item Editorial Board, \emph{Scandinavian Journal of Economics} (2021--present).
\end{itemize}
\subsection{Refereeing}
\begin{itemize}
\item \emph{American Economic Review}, \emph{Econometrica}, \emph{Quarterly Journal of Economics},
\emph{Journal of Political Economy}, \emph{Review of Economic Studies}, \emph{Journal of Public Economics},
\emph{American Economic Journal: Applied}, \emph{Economic Journal}, among others.
\end{itemize}
\subsection{Other Service}
\begin{itemize}
\item Member, Scientific Council, Institute for Evaluation of Labour Market and Education Policy (IFAU), 2022--present.
\item Expert advisor, Swedish Fiscal Policy Council (Finanspolitiska r\aa det), 2021--present.
\item Program Committee, EEA Annual Congress (2020, 2023); IIPF Congress (2022).
\end{itemize}

% ----------------------------------------------------------- SKILLS ----
\section{Languages and Technical Skills}
\textbf{Languages:}\ Swedish (native); English (fluent); German (working proficiency).\\[4pt]
\textbf{Software:}\ Stata, R, Python, Julia, \LaTeX; experience with register data (SCB), administrative microdata, and high-performance computing.

% ----------------------------------------------------------- REFERENCES ----
\section{References}
\begin{itemize}
\item \textbf{Esther Duflo} --- Abdul Latif Jameel Professor of Economics, MIT --- \href{mailto:eduflo@mit.edu}{eduflo@mit.edu}
\item \textbf{James Poterba} --- Mitsui Professor of Economics, MIT; President, NBER --- \href{mailto:poterba@mit.edu}{poterba@mit.edu}
\item \textbf{Henrik Kleven} --- Professor of Economics, Princeton University --- \href{mailto:kleven@princeton.edu}{kleven@princeton.edu}
\end{itemize}

\vspace{10pt}
\begin{center}
\footnotesize\textcolor{mutedgray}{\emph{This is a fictitious curriculum vitae created for demonstration purposes only.
The individual, publications, and affiliations described herein are not real.}}
\end{center}

\end{document}
